---
title: "BDS model: overweight-4y"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BDS model: overweight-4y}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>"
)
```

```{r setoutcome}
fn_model <- "20230525_rfr_mtry.rds"
fn_codebook <- "202211MH codebook JGZ predictors.xlsx"
outcome <- "overweight-4y"
```

```{r setmodel, eval = FALSE}
#library(ranger)
#path <- path.expand("~/Project/zonmw_kansrijke_start/WP4/modellen_CBS/20230530/Overgewicht")
#model <- readRDS(file.path(path, fn_model))
```

## Description

BDS model ``r outcome`` predicts overweight risk around the age of 4 years given child data up to the age of 4 months. The model was fitted by Mirthe Hendriks for the C4PO project using combined CBS microdata. 

This implementation is based on the random forest model version ``r fn_model`` and the code book ``r fn_codebook``. Here's a summary of the fitted model:

```
Ranger result

Call:
 ranger(overweight ~ ., data = overweight_train, num.trees = 1000,      importance = "impurity", probability = TRUE) 

Type:                             Probability estimation 
Number of trees:                  1000 
Sample size:                      13149 
Number of independent variables:  138 
Mtry:                             11 
Target node size:                 10 
Variable importance mode:         impurity 
Splitrule:                        gini 
OOB prediction error (Brier s.):  0.0761 
```

## Predictor names and importance

The model contains 138 predictors. The names of the predictor variables, ordered in terms of their importance score, are

```{r eval = FALSE}
#v <- sort(round(importance(model), 1), decreasing = TRUE)
#data.frame(importance = v)
```

```
                                    importance
bmi_4mnd_znl                             103.1
gewicht_4mnd_znl                          84.0
bmi_3mnd_znl                              64.8
gewicht_3mnd_znl                          56.5
bmi_8wks_znl                              49.6
gewicht_8wks_znl                          43.7
bmi_4wks_znl                              41.7
PRNL_birthweight                          39.3
lengte_4mnd_znl                           37.6
gewicht_4wks_znl                          36.6
lengte_3mnd_znl                           34.8
lengte_8wks_znl                           34.1
ZVWK_sumtotal_mo                          33.1
income_fa                                 32.9
lengte_4wks_znl                           32.0
income_parents                            32.0
ZVWK_hospital_mo                          31.9
ZVWK_GP_other_fa                          31.2
income_mo                                 30.9
ZVWK_GP_other_mo                          30.9
ZVWK_GP_consult_mo                        29.8
ZVWK_pharmacy_mo                          29.1
ED_woz                                    29.0
ZVWK_sumtotal_fa                          28.7
age_at_birth_mo                           27.4
ZVWK_birth_obstetrician_mo                26.3
ZVWK_birth_maternitycare_mo               26.1
SPOLIS_wages_fa                           26.0
age_at_birth_fa                           25.9
ZVWK_GP_regist_mo                         25.1
hh_vermogen                               25.0
ZVWK_GP_regist_fa                         24.1
ZVWK_GP_consult_fa                        22.9
SPOLIS_wages_mo                           22.8
SPOLIS_paidhours_fa                       21.9
SPOLIS_paidhours_mo                       21.2
ZVWK_pharmacy_fa                          20.5
income_hh                                 18.8
educationlevel_mo                         18.3
PRNL_gestational_age_week_f               17.5
ZVWK_appliances_mo                        16.7
educationlevel_fa                         15.2
ZVWK_hospital_fa                          14.9
opl1                                      11.8
ZVWK_other_mo                             10.4
ZVWK_other_fa                             10.1
opl2                                       9.7
geslacht                                   9.2
STED                                       9.1
PRNL_parity                                8.8
LAND_ETNG_fa                               8.7
ZVWK_appliances_fa                         8.1
LAND_ACHTS_fa                              6.8
ZVWK_patient_transport_lie_mo              6.8
LAND_ETNG_mo                               6.7
LAND_ACHTS_mo                              6.7
SECM_mo                                    6.7
SECM_fa                                    6.3
ZVWK_physical_other_mo                     6.2
SPOLIS_contract_mo                         5.7
SPOLIS_contract_fa                         5.6
LAND_ETNG_gebl2                            5.4
LAND_ACHTS_gebl2                           5.4
LAND_ACHTS_gebl1                           5.3
ED_rentown                                 5.2
LAND_ETNG_gebl1                            5.0
GBA_generation_fa                          4.7
income_hh_source                           4.6
house_ownership                            4.4
ZVWK_dentalcare_mo                         4.0
ZVWK_physical_therapy_mo                   4.0
ZVWK_mentalhealth_bas_mo                   4.0
residence_same_for_parents                 3.9
GBA_generation_mo                          3.8
ZVWK_mentalhealth_spec_mo                  3.7
ZVWK_mentalh_spec_nostay_inst_mo           3.5
SECM_disability_mo                         3.1
GBA_generation_kid                         3.0
premature_birth                            2.9
ZVWK_mentalh_spec_nostay_ind_mo            2.9
l_income_hh_pov_binary                     2.8
SECM_selfemployed_fa                       2.8
ZVWK_GP_basic_mo                           2.7
SECM_student_fa                            2.6
l_income_hh_min_binary                     2.5
SECM_selfemployed_mo                       2.5
SECM_otherwork_mo                          2.5
SECM_socialassistance_mo                   2.5
ZVWK_mentalhealth_bas_fa                   2.5
SECM_employee_fa                           2.4
NA_dummy_bmi_4wks_znl                      2.4
NA_dummy_bmi_4mnd_znl                      2.4
l_income_hh_pov_4j_binary                  2.3
l_income_hh_min_4j_binary                  2.3
SECM_unemployed_mo                         2.3
ZVWK_dentalcare_fa                         2.3
ZVWK_abroad_fa                             2.3
ZVWK_GP_basic_fa                           2.2
ZVWK_patient_transport_lie_fa              2.2
NA_dummy_SPOLIS_wages_mo                   2.2
SECM_employee_mo                           2.1
SECM_otherwork_fa                          2.1
SECM_unemployed_fa                         2.1
SECM_disability_fa                         2.0
NA_dummy_SPOLIS_wages_fa                   2.0
PRNL_multiples                             1.9
ZVWK_abroad_mo                             1.9
NA_dummy_income_hh                         1.9
ZVWK_physical_therapy_fa                   1.8
SECM_student_mo                            1.7
ZVWK_mentalhealth_spec_fa                  1.7
SECM_otherassistance_fa                    1.6
NA_dummy_ZVWK_mentalh_spec_other_fa        1.6
SECM_director_fa                           1.5
ZVWK_physical_other_fa                     1.5
NA_dummy_ZVWK_GP_basic_fa                  1.5
SECM_familywork_fa                         1.4
ZVWK_mentalh_spec_nostay_inst_fa           1.4
SECM_otherassistance_mo                    1.3
SECM_socialassistance_fa                   1.2
NA_dummy_ZVWK_GP_basic_mo                  1.1
NA_dummy_ZVWK_mentalh_spec_other_mo        1.1
SECM_familywork_mo                         1.0
NA_dummy_income_mo                         1.0
SECM_retirement_mo                         0.9
SECM_retirement_fa                         0.9
ZVWK_mentalh_spec_nostay_ind_fa            0.9
ZVWK_patient_transport_sit_mo              0.5
ZVWK_birth_obstetrician_fa                 0.5
NA_dummy_income_fa                         0.5
ZVWK_birth_maternitycare_fa                0.4
NA_dummy_age_at_birth_fa                   0.4
SECM_director_mo                           0.3
ZVWK_mentalhealth_spec_stay_fa             0.3
ZVWK_mentalhealth_spec_stay_mo             0.0
ZVWK_mentalh_spec_other_mo                 0.0
ZVWK_patient_transport_sit_fa              0.0
ZVWK_mentalh_spec_other_fa                 0.0
```

## Connection between predictors and Basisdataset

Not all predictors are defined in the Dutch Basisdataset and many variables have low importance scores. 

The following table describes the relevant fields defined by the Dutch Basisdataset for a subset for most important predictors.

| Variabele                  | BDS               |JAMES| Imp | In | Comments          |
|----------------------------|-------------------|-----|-----|----|-------------------|
| BMI                        | 235, 245, 724, 20 | Y   | 103 | Y  | check             |
| weight                     | 245, 724, 20      | Y   | 84  | Y  | check             |
| PRNL_birthweight           | 110               | Y   | 39  | Y  | check             |
| length/height              | 235, 724, 20      | Y   | 38  | Y  | check             |
| ZVWK_sumtotal_mo           |                   | N   | 33  | N  | not available     |
| income_fa                  |                   | N   | 33  | N  | not available     |
| income_parents             |                   | N   | 32  | N  | not available     |
| income_mo                  |                   | N   | 31  | N  | not available     |
| ED_woz                     |                   | N   | 29  | Y  | derive from PC4   |
| ZVWK_sumtotal_fa           |                   | N   | 29  | N  | not available     |
| age_at_birth_mo            | 63, 62, 20        | Y   | 27  | Y  | check             |
| age_at_birth_fa            | 63, 62, 20        | Y   | 26  | Y  | check             |
| SPOLIS_paidhours_fa        |                   | N   | 22  | N  | not available     |
| SPOLIS_paidhours_mo        |                   | N   | 21  | N  | not available     |
| PRNL_gestational_age       | 82                | Y   | 18  | Y  | check             |
| educationlevel_mo          |                   | N   | 18  | N  | duplicate         |
| educationlevel_fa          |                   | N   | 15  | N  | duplicate         |
| opl1                       | 66, 62            | N   | 12  | Y  | check             |
| opl2                       | 66, 62            | N   | 10  | Y  | check             |
| sex                        | 19                | Y   | 9   | Y  | check             |
| PRNL_parity                | 741               | N   | 9   | Y  | check             |
| STED                       | 16                | Y   | 9   | Y  | derive from PC4   |
| LAND_ETNG_gebl1            | 71, 62            | Y   | 9   | Y  | check             |
| LAND_ACHTS_gebl1           | 71, 62            | N   | 9   | N  | duplicate         |
| LAND_ETNG_gebl2            | 71, 62            | Y   | 7   | Y  | check             |
| LAND_ACHTS_gebl2           | 71, 62            | N   | 7   | N  | duplicate         |
| GBA_generation_fa          |                   | N   | 5   | N  | low imp           |
| ED_rentown                 |                   | N   | 5   | N  | low imp           |
| GBA_generation_mo          |                   | N   | 4   | N  | low imp           |
| residence_same_for_parents |                   | N   | 4   | N  | low imp           |
| GBA_generation_kid         |                   | N   | 3   | N  | low imp           |
| premature_birth            | 82                | N   | 3   | N  | duplicate         |
| SECM\_{xxx}                |                   | N   | 3   | N  | low imp           |
| PRNL_multiples             | 108               | N   | 2   | N  | low imp           |
| birth date                 | 20                | Y   | \-  | N  | not in model      |
| measurement date           | 724               | Y   | \-  | N  | not in model      |
| height mother              | 238               | Y   | \-  | N  | not in model      |
| height father              | 240               | Y   | \-  | N  | not in model      |
| weight mother              |                   | N   | \-  | N  | not in model      |
| weight father              |                   | N   | \-  | N  | not in model      |
| smoking pregnancy          | 91                | Y   | \-  | N  | not in model      |

The table maps the overlap between two data sources: BDS (and accessible through JAMES) and the CBS data used to create the model. Predictors are ordered in terms of the importance score. The column `In` specifies which predictors are selected to be included into a compressed model with 15 predictors (12 fixed, 3 time-varying). The most important variables (child `BMI`, `weight` and `height`) are available for personal risk prediction. Income variables are not available, but a `ED_woz` value for the PC4 postal code is a reasonable proxy to parental income. Age of parents at birth, gestational age and parental education are included, and well as some of the less important variables (sex, parity, parental birth country).

Note that importance scores vary depending on what other variables are in the model, so for a proper picture of variable importance, we need to refit the model using the subset of the 15 predictors.

## Predictor codings

In other to be able to apply the random forest model in practice, it is vital that the variable codings used in the CBS-model and JAMES-model match.

Here is a proposal for variable coding in both models:

| JAMES | CBS name              | Code| Description                                   |
|-------|-----------------------|-----|-----------------------------------------------|
|`bmi_z`| `BMI_{time}_znl`      |     | Body Mass Index, Z-score (AGD::nl4.bmi)       |
|`hgt_z`| `lengte_{time}_znl`   |     | Length/height, Z-score (AGD::nl4.hgt)         |
|`wgt_z`| `gewicht_{time}_znl`  |     | Weight, Z-score (AGD::nl4.wgt)                |
| `age` |                       |     | Decimal age: round((date - dob) / 365.25, 4)  |
| `bw`  | `PRNL_birthweight`    |     | Birth weight (grammes)                        |
| `woz` | `ED_woz`              |     | WOZ value - immovable property (EURO)         |
| `agem`| `age_at_birth_mo`     |     | Mother age at child's birth (years)           |
| `agef`| `age_at_birth_fa`     |     | Father age at child's birth (years)           |
| `ga`  | `PRNL_gestational_age`|     | Gestational age (completed weeks)             |
| `eduf`| `opl1`                |     | Level of education, biol father (number)      |
|       |                       | 1   | None                                          |	
|       |                       | 2   | Basis                                         |
|       |                       | 3   | MLK/VMBO-LWOO/LBO/VBO/VMBO-BBL&KBL            |	
|       |                       | 4   | MAVO/VMBO/GL&TL                               |
|       |                       | 5   | MBO                                           |
|       |                       | 6   | HAVO/VWO                                      |
|       |                       | 7   | HBO/HTS/HEAO                                  |
|       |                       | 8   | WO                                            |
|       |                       | `NA`| Other (98), unknown (00)                      |
| `edum`| `opl2`                |     | Level of education, biol mother (number)      |
|       |                       |     | See `opl1` codes                              |
| `sex` | `geslacht`            |     | Sex of child (number)                         |
|       |                       | 1   | Male                                          |
|       |                       | 0   | Female                                        |
|       |                       | `NA`| Unknown, undetermined                         |
| `par` | `PRNL_parity`         |     | Number of births (GA >=16w), inc this (number)|
| `urb` | `STED`                |     | Urbanisation grade (number)                   |
|       |                       | 1   | >= 2500 addresses/km^2                        |
|       |                       | 2   | 1500-2500 addresses/km^2                      |
|       |                       | 3   | 1000-1500 addresses/km^2                      |
|       |                       | 4   |  500-1000 addresses/km^2                      |
|       |                       | 5   | < 500 addresses/km^2                          |
|       |                       | `NA`| Unknown                                       |
| `ctrf`| `LAND_ACHTS_gebl1`    |     | Country of birth, biological father (factor)  |
|       |                       | 1   | Netherlands                                   |
|       |                       | 2   | EU-15, other developed economies              |
|       |                       | 3   | New EU-countries, economies in transition     |
|       |                       | 4   | Northern Africa                               |
|       |                       | 5   | East Asia                                     |
|       |                       | 6   | Other Africa, Asia, Latin America             |
|       |                       | 7   | Surinam and (former) Nederlands Antilles      |
|       |                       | 8   | Turkey                                        |
|       |                       | 9   | Unknown                                       |
| `ctrm`| `LAND_ACHTS_gebl2`    |     | Country of birth, biological mother (factor)  |
|       |                       |     | See `LAND_ACHTS_gebl1` codes                  |


## Strategy to deal with missing predictor values

We still have to devise a strategy here.
